Basics of Hardware Cache Optimization

### 2017-05-30 paper.tex
Revise, tweak, expand
Add new measurement; revise, expand, and tweak
Exclude some stuff from the article

% Use a consitent group/thousands separator for siunitx and pgf.
\pgfkeys{/pgf/number format/.cd,
   set thousands separator=\,
}
% \sisetup{
%    group-separator={,}
% }

@@

@@

\input{tex/intro}
\input{tex/motivation}
\input{tex/types}
\input{tex/basic-concepts}

\section{Example: \texttt{std::vector} vs. \texttt{std::list}}
\label{sec:vvl}

@@

\begin{listing}
   \inputminted[firstline=8]{c}{array-sum/array-sum.c}
   \caption{This is C code}
   \label{lst:array-sum}
\end{listing}

% This program is likely to have excellent spatial locality: the array...

% \begin{figure}[htb]
\begin{figure}
   \centering
   \begin{tikzpicture}
      \datavisualization
      [scientific axes=clean,
       x axis={label={Array size (KiB)}, length=0.8\textwidth},
       y axis={label={Processor time (ms)}, length=6cm},
       visualize as scatter,
       scatter={style={mark=*, mark options={scale=.65}}}]
         % See <https://tex.stackexchange.com/q/198323>.
         data [read from file=array-sum/size-time.csv, separator=\space];
   \end{tikzpicture}
   \caption{This figure took way too long to create}
   \label{fig:array-sum}
\end{figure}

% See \cref{fig:array-sum}.  What's going on here?

>>>>

% Use a consitent group/thousands separator for siunitx and pgf.
\pgfkeys{%
   /pgf/number format/.cd,
   1000 sep={\,},
   min exponent for 1000 sep=4,
}
% \sisetup{
%    group-separator={,}
% }

@@

% X (cross) something out.  See <https://tex.stackexchange.com/a/276698>.
\newcommand{\x}[1]{\ignorespaces}

@@

\input{tex/intro}
\input{tex/motivation}
% \section{Hardware Caches} % Cache, Structure of Caches
\input{tex/operation}
\input{tex/types}
\input{tex/key-concepts}
\section{Example: \texttt{std::vector} vs. \texttt{std::list}}
\label{sec:vvl}

@@
